---
title: 'test2'
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### R-program / Spanning Test of Bitcoin 
 ---
  variable | Ticker | explanation 
 :-------- | :----- | :-------------
 yi0       |BTC     |Bitcoin   
 yi1       |TSLA    |Tesla, Inc   
 yi2       |SOXX    |iShares Trust - iShares Semiconductor ETF   
 yi3       |VOO     |Vanguard S&P 500 ETF   
 xi1       |DBC     |Invesco DB Commodity Index Tracking Fund     
 xi2       |GLD     |SPDR Gold Shares     
 xi3       |QQQ     |Invesco QQQ Trust  
 xi4       |SPY     |SPDR S&P 500 ETF Trust     
 xi5       |TLT     |iShares 20+ Year Treasury Bond ETF     
 
This is the price from yahoo.finance. For more details on price see <http://finance.yahoo>.  
Risk free T-bill : Market Yield on U.S. Treasury Securities at 1-Month Constant Maturity (DGS1MO)
Start date : mm/dd/yyyy ???

```{r ,echo=FALSE,message=FALSE}
# install.packages('rmarkdown')
# install.packages('tinytex')
# tinytex::install_tinytex() # install TinyTeX

library(dplyr)
library(car)
library(lmtest)
library(tidyverse)
library(data.table)
```



```{r }


csvfile <-'data002.csv'
# Store the csv file into the data frame of "df"
df <- read.csv(csvfile)
# Show the first five rows
head(df)
# summary(df)
df01 <- transmute(df, 
          Date = Date,
          BTC = ( BTC - shift(BTC)) / shift(BTC) * 100 - Tbill,
          DBC = ( DBC - shift(DBC)) / shift(DBC) * 100 - Tbill,
          GLD = ( GLD - shift(GLD)) / shift(GLD) * 100 - Tbill,
          QQQ = ( QQQ - shift(QQQ)) / shift(QQQ) * 100 - Tbill,
          SPY = ( SPY - shift(SPY)) / shift(SPY) * 100 - Tbill,
          TLT = ( TLT - shift(TLT)) / shift(TLT) * 100 - Tbill)

head(df01)



```



```{r }
############################################################
# test Bitcoin-usd
# ols01 <- lm(yi0 ~ xi1 + xi2 + xi3 + xi4 + xi5 , data = df)
# summary(ols01)

ols0 <- lm(BTC ~ DBC + GLD + QQQ + SPY + TLT , data = df01)
summary(ols0)
# bptest(ols0) #BP-Test 

lhs <- rbind(c(1,0,0,0,0,0),c(0,1,1,1,1,1))

lht(ols0,lhs,c(0,1))

ggplot() +
   geom_point(mapping=aes(x=Date, y=BTC), data=df01)

df01 %>% 
  ggplot(aes(x=Date, y=BTC)) +
  geom_point(size = 0.9) +
  geom_smooth(formula = y ~ x, method = "lm", se = FALSE) + 
  # method = "lm" : linear regerssion 
  labs(
    x = "Date(2014 - 2021)",
    y = "Excess Return of BTC "
  )

############################################################
# test Tesla
# ols1 <- lm(yi1 ~ xi1 + xi2 + xi3 + xi4 + xi5 , data = df)
# summary(ols1)
# lhs <- rbind(c(1,0,0,0,0,0),c(0,1,1,1,1,1))
# lht(ols1,lhs,c(0,1))
# 
# ############################################################
# test semicondutor industry etf
# ols2 <- lm(yi2 ~ xi1 + xi2 + xi3 + xi4 + xi5 , data = df)
# summary(ols2)
# lhs <- rbind(c(1,0,0,0,0,0),c(0,1,1,1,1,1))
# lht(ols2,lhs,c(0,1))

############################################################
# test VOO - bangard S&P 500
# Hypothesis: (Intercept) = 0 ,xi1  + xi2  + xi3  + xi4  + xi5 = 1
# ols3 <- lm(yi3 ~ xi1 + xi2 + xi3 + xi4 + xi5 , data = df)
# summary(ols3)
# lhs <- rbind(c(1,0,0,0,0,0),c(0,1,1,1,1,1))
# lht(ols3,lhs,c(0,1))


```

